---
title: "T-Test Problem"
author: "Jose Trejo"
date: "Spring, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(tigerstats)
Ourdata <- read.csv(file="GSScsv.csv")
```


## Is there a difference in  average years of education (EDUC) between the those who did or did not vote in 2012 (VOTE12)?

$H_0$ No difference in average years of education between those who voted in 2012 and those who did not vote. 

$H_a$ There is a difference in average years of education between those who voted in 2012 and those who did not. 

## Graphical Summary 

```{r}
boxplot(EDUC~VOTE12, data=Ourdata)
```

It appears that the average years of education between those who voted in 2012 is a little more higher than those who did not vote. 

## Numerical Summary 

```{r}
favstats(EDUC~VOTE12, data=Ourdata)
```

## Inferential test

```{r}
t.test(EDUC~VOTE12, data=Ourdata)
```

## Conclusion
The p-value from the t-test is 0.005, this is less than 0.05, so we reject the null hypothesis and conclude we have evidence that there is a difference between the average years of education for those who voted in 2012and those who didn't vote in 2012.